Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-08-31 Paper1.tex
Final version paper 31.08.2022

For completeness, we now briefly describe the self-consistency F-DMFT scheme used.
(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
%  
\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
\end{split}
\end{equation}
% 
(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
is given by
%
\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
\end{equation}   
%  
where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$. (v) The nonequilibrium many-body impurity problem is solved according to the procedure described below, leading to the new $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.

Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one should solve a time-periodic impurity problem leading to a non-diagonal SE. However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the 
 phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the phonon SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are sufficiently suppressed with respect to the diagonal ones}. 
Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}. The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

@@

We set off by analyzing the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.

In Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a), the photocurrent $j$ increases as a function of the driving frequency $\Omega$ within the range $4\lesssim\Omega\lesssim8$ independent of the value of $v$. According to the discussion in Sec.~\ref{sec:scheme_only_electrons} (cf.  Fig.~\ref{fig:energy_setup}), this $\Omega$-range is expected to allow only for DEs. The current in this range  increases with increasing $v$. Similarly, the double occupation shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) increases as a function of the driving frequency~\footnote{Notice that the increase of $N_{\text{D}}$ in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) as compared to Ref.~\cite{so.do.18} is not as steep and large in magnitude. This is due to our setup, where every photoexcited carrier can escape into the right lead.}.

>>>>

For completeness, we now briefly describe the self-consistency F-DMFT scheme used.
(i) We start from an initial guess for the electron SE $\kel{\mat{\Sigma}}(\omega)$ and set $\kel{\mat \Sigma}_{\text{e-ph}}(\omega)=0$. (ii) Then we compute the local electron GF as 
%  
\begin{equation}\label{eq:Lat_LocGF}
\begin{split}
\kel{\mat G}_{\text{loc}}(\omega) &= \int \dd\epsilon \int \dd\overline{\epsilon} \ \rho(\epsilon,\overline{\epsilon}) \times \\ 
&\times \left[\kel{\mat G}^{-1}_{0}(\omega,\epsilon,\overline{\epsilon}) - \kel{\mat\Sigma}(\omega) - \kel{\mat \Sigma}_{\text{e-ph}}(\omega) \right]^{-1}.
\end{split}
\end{equation}
% 
(iii) Using Eq.~\eqref{eq:backbone_e-ph_SE}, we obtain the phonon contribution to the e-ph SE $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$.
(iv) The problem is mapped onto a single impurity plus bath, whose hybridization function
is given by
%
\begin{equation}\label{eq:imp_Dyson_eq}
\kel{\mat{\Delta}}(\omega) = \kel{\mat{g}}^{-1}_{0,\text{site}}(\omega) - \kel{\mat{G}}^{-1}_{\text{loc}}(\omega) - \kel{\mat{\Sigma}}(\omega),
\end{equation}   
%  
where $\kel{\mat{g}}^{-1}_{0,\text{site}}(\omega)$ is defined as in Eq.~\eqref{eq:inv_non-int_lat_GF_comps} with $\varepsilon_{mn}(\epsilon,\overline{\epsilon})=0$. (v) The nonequilibrium many-body impurity problem is solved according to the procedure described below, leading to the new $\kel{\mat{\Sigma}}(\omega)$. (vi) We insert the electron and e-ph SEs into step (ii) and iterate the steps (ii)-(vi) until convergence.

Eq.~\eqref{eq:imp_Dyson_eq} gives a bath hybridization function $\kel{\mat\Delta}(\omega)$ whose periodic time-dependence is encoded in its Floquet structure. 
This means that, in principle, one should solve a time-periodic impurity problem leading to a non-diagonal SE. However, in Ref.~\cite{so.do.18} it was argued and shown that for the considered electric field amplitudes, off-diagonal terms in the electron SE $\kel{\mat{\Sigma}}(\omega)$ can be safely neglected with respect to the diagonal ones. We follow this argument and adopt here 
this Floquet-diagonal self-energy approximation (FDSA) as well. In addition, it turns out that also for the e-ph SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ this approximation is justified~\footnote{More specifically, we verified that in the parameter range in which FDSA is justified for the electron SE $\kel{\mat{\Sigma}}(\omega)$ (Sec.~\ref{sec:results}), the off-diagonal terms of the e-ph SE $\underline{\bf{\Sigma}}_{\text{e-ph}}(\omega)$ are sufficiently suppressed}.   
Consequently, we  solve a nonequilibrium stationary impurity problem, by considering only the $(0,0)$-Floquet matrix element of all the quantities in Eq.~\eqref{eq:imp_Dyson_eq}. The other diagonal components of the SEs are then reconstructed by using the property $\kel{\Sigma}_{mm}(\omega) = \kel{\Sigma}_{00}(\omega+m\Omega)$.

@@

We start by analyzing the case without e-ph interaction and address the behavior of the physical quantities as functions of $\Omega$ for different values of the lead-layer hybridization.

In Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(a), the photocurrent $j$ increases as a function of the driving frequency $\Omega$ within the range $4\lesssim\Omega\lesssim8$. According to the discussion in Sec.~\ref{sec:scheme_only_electrons} (cf.  Fig.~\ref{fig:energy_setup}), this $\Omega$-range is expected to allow only for DEs. The current in this range  increases with increasing $v$. Similarly, the double occupation shown in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) increases as a function of the driving frequency~\footnote{Notice that the increase of $N_{\text{D}}$ in Fig.~\ref{fig:j_vs_omega_mu1_v_0.4_0.8_eph}(b) as compared to Ref.~\cite{so.do.18} is not as steep and large in magnitude. This is due to our setup, where every photoexcited carrier can escape into the right lead.}.

### 2022-08-31 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_11_eph.tex
Final version paper 31.08.2022

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];

@@

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{el};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{el+ph};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11ph,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11ph and xaxis,soft clip={domain=-15:15}];

>>>>

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.4O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11ph,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.4O11ph.dat' u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11ph and xaxis,soft clip={domain=-15:15}];

@@

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{el};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{el+ph};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11.dat' u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.8O11ph.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11ph,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
plot './neq_distr_f_filling_hyb0.8O11ph.dat' u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11ph and xaxis,soft clip={domain=-15:15}];

### 2022-08-31 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
Final version paper 31.08.2022

%\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
%\addlegendentry{$v=0.4$};
%\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
%\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];

@@

\addlegendimage{solid,color=hcoral,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hlime,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hcoral,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hcoral,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hlime,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hlime,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hcoral,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hlime,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];

>>>>

%\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
%\addlegendentry{$v=0.4$};
%\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
%\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O5,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O5.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.8O5.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O5,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.8O5.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O5 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O5 and xaxis,soft clip={domain=-15:15}];

@@

\addlegendimage{solid,color=hblue,scale={1.0},line width=1pt}
\addlegendentry{$v=0.4$};
\addlegendimage{solid,color=hred,scale={1.0},line width=1pt} 
\addlegendentry{$v=0.8$};

@@

\addplot[solid,raw gnuplot,color=hblue,line width=1pt] gnuplot {
plot './Green_hyb0.4O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.4O11,solid,raw gnuplot,color=hblue,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.4O11.dat" u 1:3 w l;
};

\addplot[solid,raw gnuplot,color=hred,line width=1pt] gnuplot {
plot './Green_hyb0.8O11.dat' u 1:(-1/3.1415)*($3) w l;
};

\addplot[name path=neq_distr_f_filling_hyb0.8O11,solid,raw gnuplot,color=hred,line width=1pt,opacity=0.0] gnuplot {
plot "neq_distr_f_filling_hyb0.8O11.dat" u 1:3 w l;
};

\path[name path=xaxis] (axis cs:-15,0) -- (axis cs:15,0);
\addplot [fill=hblue,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.4O11 and xaxis,soft clip={domain=-15:15}];
\addplot [fill=hred,fill opacity=0.5] fill between[of=neq_distr_f_filling_hyb0.8O11 and xaxis,soft clip={domain=-15:15}];
